Analysis of Bauer et al. (2023) bioRxiv: <br> Persistence

### 2023-03-01 R/model_check_persistence.Rmd
Update model_check_persistence.Rmd

```{r dharma, collapse = TRUE}
m_1 %>% DHARMa.helpers::dh_check_brms(integer = TRUE)
m_2 %>% DHARMa.helpers::dh_check_brms(integer = TRUE)
```

>>>>

```{r dharma, collapse = TRUE, fig.height = 4}
m_1 %>% DHARMa.helpers::dh_check_brms(integer = TRUE)
m_2 %>% DHARMa.helpers::dh_check_brms(integer = TRUE)
```
